Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus

### 2023-09-05 manuscript_thev_transcriptome.Rmd
reorganize scripts to make reg-by-reg data  tables

## load in variables to be used inline 
source("scripts/r/bam_file_analysis.R")
source("scripts/r/thev_splicing_fullMap.R")

@@

**Early Region 1 (E1) transcripts**. This region in MAdVs is the first transcribed after successful entry of the viral DNA into the nucleus of the host cell but at low levels [@Zhao2014]. The host transcription machinery is solely responsible for the transcription of this region. After their translation, the E1 proteins in concert with a myriad of host transcription factors activate the other viral promoters [@Guimet2016]. We discovered four novel transcripts in this region with varying protein-coding potential (PCP).

@@

Early Region 2A (E2A) transcripts.

@@

>>>>

## load in variables to be used inline 
source("scripts/r/bam_file_analysis.R")
source("scripts/r/thev_splicing_fullMap.R")
source("scripts/r/abundance_analyses.R")

@@

**Early Region 1 (E1) transcripts**. This region in MAdVs is the first transcribed after successful entry of the viral DNA into the nucleus of the host cell but at low levels [@Zhao2014]. The host transcription machinery is solely responsible for the transcription of this region. After their translation, the E1 proteins in concert with a myriad of host transcription factors activate the other viral promoters [@Guimet2016]. Only two ORFs (ORF1 [sialidase] and Hyd) are predicted in this region; however, we discovered four novel transcripts in this region (__Figure 5__). The abundance of the transcripts and splice junctions varied over time. The most abundant was #### at #### and

@@

Early Region 2A (E2A) transcripts.
some with multiple protein-coding potential (PCP)

@@

```{r region-by-region_e1_figure}
set_flextable_defaults(font.size = 8)
flextable(reg_e1_brkdown) %>% theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed",
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::font(part = "all", fontname = "Avenir") %>%
  flextable::set_header_labels(start = "Start", end = "End",
                               splice_site = "Splice Site", region = "Region",
                               strand = "Strand", trxpt_id = "Transcript ID",
                               coding_potential = "Protein Coding Potential",
                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
                               "72hpi" = "72h.p.i") %>%
  flextable::width(., width = 0.6) %>%
  flextable::align(align = "center", part = "all") %>%
  add_header_row(., values = c("", "Splice Junction", "", "", "Junction Reads", ""),
                 colwidths = c(1, 4, 1, 1, 4, 1)) %>%
  flextable::vline(j = c(1, 5, 7, 11), border = fp_border_default(color = "grey",
                                                                  width = 1.5))
```
